### 2014-02-28 paper/real.tex
wip

We refer the interested reader to~\tocite{icfp,haskellsymp} for
additional details on the various implementations of this system.
%
Finally, we remark that in this work unifies these systems and
presents in addition to proving NI fo such systems with asynchronous
communication primitives.

@@

>>>>

We refer the interested reader to~\tocite{icfp,haskellsymp} for
additional details on the various implementations of this system.
%
Here, we lastly remark that our work unifies these systems and
presents a proof of NI for such systems with asynchronous
communication primitives.

@@

JavaScript (JS), as specified by ECMAScript~\tocite{}, does not have any
built-in functionality for I/O.
%
Consequently, and in contrast to our C and Haskell embeddings, for
which we must eliminate external effects, the embedding for JS is
trivial.
%
Hence, as a first step, we implement the IFC language functionality in the
JS runtime and expose the new functions, e.g., |fork|, by attaching
them to the JS global object.
%
Importantly, each task runs a separate instances of this runtime.

Indeed this coarse-grained approach is already used by browsers in the
Worker API~\tocite{}, which provides client-side JS with primitives
for executing code in a separate thread, called a Worker.
%
Each Worker has a separate runtime with a fresh global object.
%
In turn, exchanging information between runtimes is accomplished with
message-passing, i.e., \texttt{postMessage}.
%
The message-passing approach is, in part, due to ECMAScript's lack
of well-defined semantics for concurrency.
%
Hence sharing and accessing objects such as the DOM across threads is
undefined.
%

Hence, our implementation provides

\begin{itemize}
\item not completely unrealist; workers provide a similar world; we
  provide labeled workers

\item actual embeddings of JS have external effects; consider the browser
  case as in SWAPI
\begin{itemize}
   \item associate label with browsing context ~ task
   \item use CSP and sandbox flags to control external effects
   \item mediate communication by interposing on on postMessage
   argue that browsers already have to provide isolation guarantees
   between different compartments
\end{itemize}

\item talk about SWAPI's attach object feature that makes the concrete
  implementation more interesting
\end{itemize}

Of course, applications, such as browsers, that embed JavaScript
expose various features that perform external effects (again by
attaching them as objects to the JS global object).
%
